%----------------------- Weekly Progress Document ------------------------
%
% Created by: Shane Reynolds 2020-02-29
%
%-------------------------------------------------------------------------

%-------------- Preamble
\documentclass[12pt]{article}
\input{preamble/weekly_progress_preamble} % this must be left as \input, \include wont work in the preamble

%-------------- Information For The Title Page
\title{	
		Thesis Progress Form\\
		CHARLES DARWIN UNIVERSITY\\
		College of Engineering, IT, and Environment
	  }
\author{}
\date{}

%------------------------ Main Document --------------------------
\begin{document}
	
	\maketitle
	
	\begin{namelist}{xxxxxxxxxxxx}
		\item[{\bf Name:}]
			Shane Reynolds
		\item[{\bf Unit:}]
			ENG720
		\item[{\bf Title:}]
			Automatic generation control of a two area power system using deep reinforcement learning
		\item[{\bf Supervisors:}]
			Charles Yeo \& Stefanija Klaric
		\item[{\bf Time \& Date:}] No meeting took place
			
	\end{namelist}
	
	\pagestyle{plain} % get rid of fancy headers
	\textheight = 565pt % hack to include page numbers
	
	%-------------- Sections
	\section{Progress since last meeting}
	This is the first meeting
	
	\section{Discussion Points}
		\begin{itemize}
			\item Emailed SK on 02/03/2020 to confirm second supervisor position
			
			\item Emailed CY on 02/03/2020 to arrange Week 1 meeting, and provide with draft copy of thesis supervision agreement
			
			\item Emailed CY to follow up on initial meeting. Unable to get in contact.
			
			\item CY return email on 05/03/2020 requesting initial meeting for 12/03/2020. Accepted and sent calendar invite. CY accepted, but can only provide phone contact.
			
			\item CY returned signed copy of Thesis supervision agreement. SK still to sign.
			
			\item Only email communication has occurred or Week 1.
			
			\item Revised draft research proposal to correct errors, completed referencing, tighten up language, and reformat.
			
			\item Enquire at power utility for data.
			
			\item Investigate simulation packages.
		\end{itemize}
	
	\section{Plan until the next meeting}
	\begin{itemize}
		\item Revise research proposal deliverable further
		
		\item Commence research for literature review
		
		\item Commence writing literature review
		
		\item Investigate ways to synthesise data
		
		\item Develop a data management plan
		
		\item Investigate programming languages for Deep Reinforcement Learning
		
	\end{itemize}
	
	%-------------- Supervisor sign-off
	\par
	\vspace{\fill}
	\noindent\rule{0.4\linewidth}{0.5pt}%
	\vspace{1em}%
	\par
	\noindent\textbf{Supervisor}\vspace{1em}%
	\par
	\noindent\today

\end{document}