%----------------------- Weekly Progress Document ------------------------
%
% Created by: Shane Reynolds 2020-02-29
%
%-------------------------------------------------------------------------

%-------------- Preamble
\documentclass[12pt]{article}
\input{preamble/weekly_progress_preamble} % this must be left as \input, \include wont work in the preamble

%-------------- Information For The Title Page
\title{	
		Thesis Progress Form\\
		CHARLES DARWIN UNIVERSITY\\
		College of Engineering, IT, and Environment
	  }
\author{}
\date{}

%------------------------ Main Document --------------------------
\begin{document}
	
	\maketitle
	
	\begin{namelist}{xxxxxxxxxxxx}
		\item[{\bf Name:}]
			Shane Reynolds
		\item[{\bf Unit:}]
			ENG720
		\item[{\bf Title:}]
			Automatic generation control of a two area power system using deep reinforcement learning
		\item[{\bf Supervisors:}]
			Charles Yeo \& Stefanija Klaric
		\item[{\bf Time \& Date:} \today \ @ 1pm]
			
	\end{namelist}
	
	\pagestyle{plain} % get rid of fancy headers
	\textheight = 565pt % hack to include page numbers
	
	%-------------- Sections
	\section{Progress since last meeting}
	\begin{itemize}
		\item Investigated priority experience replay, which provides a metric describing the usefulness of each experience tuple collected by the agent during training. This was a technique that was used by a research group in Singapore, which seemed to improve the performance of the agent.
		\item Ran an experiment for 20000 episodes using the standard original DDPG implementation. The result did not show any material improvement over training the agent.
		\item Implemented a prioritised experience replay memory system for the agent and ran an experiment for 10000 episodes. Experiment has not yet concluded at the time of the meeting. 
	\end{itemize}
	\section{Discussion Points}
	\begin{itemize}
		\item Outlined recent progress to CY, as described above.
		\item Asked CY if there was any feedback regarding the thesis document. CY acknowledged that existing document does not need any improvement.
	\end{itemize}
	\section{Plan until the next meeting}
	\begin{itemize}
		\item Assess agent performance upon conclusion of the most recent experiment using priority experience replay and assess if the implementation of a supervised learning using training data from a tuned PID controller will need to be used.
		\item Reach out to research group in NTU to obtain better ideas on the approach taken to achieving performance gains over standard PID control.
	\end{itemize}
	%-------------- Supervisor sign-off
	\par
	\vspace{\fill}%
	\noindent\rule{0.4\linewidth}{0.5pt}%
	\vspace{1em}%
	\par
	\noindent\textbf{Supervisor}\vspace{1em}%
	\par
	\noindent\today

\end{document}